Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-01 WSSSPE3/report/wg_appendix_software_credit.tex
Moved sentence from SC appendix to main section

Modern scientific research relies considerably on software, and ensuring that
developers of such scientific software receive credit for their efforts will
encourage additional creation and maintenance. \katznote{the prev sentence is
good, but feels a bit odd in the middle of the appendix, rather than at the
beginning} There currently is no standard mechanism for citing software or
receiving credit for software (akin to publications/citations). Software is
eligible for DOI assignment, but DOI metadata fields are not well tuned or
standardized for software (vs.\ publications). Some software providers apply for
DOIs, but this is not widely adopted. Also, there is no mechanism to cite
software dependencies within software.

>>>>

There currently is no standard mechanism for citing software or
receiving credit for software (akin to publications/citations). Software is
eligible for DOI assignment, but DOI metadata fields are not well tuned or
standardized for software (vs.\ publications). Some software providers apply for
DOIs, but this is not widely adopted. Also, there is no mechanism to cite
software dependencies within software.

### 2015-12-01 WSSSPE3/report/wg_main_software_credit.tex
Moved sentence from SC appendix to main section

Science and engineering research increasingly relies on software, but there is
currently no standard mechanism for citing software or receiving credit for
developing software akin to receiving credit via citations for writing papers.
Standardizing software citations offers one route to establishing such a
citation and credit mechanism. Software is currently eligible for DOI
assignment, but DOI metadata fields are not well tuned for software compared to
publications. Some software providers apply for DOIs but it is still not widely
adopted. Also, there is no mechanism to cite software dependencies within
software in the same way papers cite supporting prior work.

>>>>

Modern scientific and engineering research relies considerably on software, 
but currently no standard mechanism exists for citing software or receiving 
credit for developing software akin to receiving credit via citations for 
writing papers. Ensuring that developers of such scientific software receive 
credit for their efforts will encourage additional creation and maintenance. 
Standardizing software citations offers one route to establishing such a
citation and credit mechanism. Software is currently eligible for DOI
assignment, but DOI metadata fields are not well tuned for software compared to
publications. Some software providers apply for DOIs but it is still not widely
adopted. Also, there is no mechanism to cite software dependencies within
software in the same way papers cite supporting prior work.
